---
title: "longirt2563"
author: "Jiewen Tsai"
date: '2021-05-09'
tags:
- R
- IRT
---

> The content of this doc is not complete. But the part of bibliometrix process may be useful to refer to later.

```{r message = FALSE}
library(bibliometrix)
library(tidyverse)
```

## 1 Data loading and converting

```{r}
lirt2563 <- convert2df(
  file = "longirt2563.bib", 
  dbsource = "scopus", 
  format = "bibtex"
  )
```

## 2 Bibliometric Analysis

### 2.1 basic summary and plot

```{r}
res_lirt2563 <- biblioAnalysis(lirt2563, sep = ";")
summary(res_lirt2563, k = 10, pause = FALSE)
plot(res_lirt2563, k = 10, pause = FALSE)
```

### 2.2 keywords growth

It calculates yearly occurrences of top keywords/terms.

```{r}
KeywordGrowth(lirt2563, Tag = "ID", sep = ";", top = 10, cdf = T) %>%
  reshape2::melt(id='Year') %>%
  mutate(Year = as.factor(Year)) %>%
  ggplot(aes(Year,value, group=variable, color=variable)) + geom_line()
```

## 3 Bibliographic network matrices

### 3.1 co-citation network (references)

```{r}
# Create a co-citation network

#cocitation_lirt2563 <- biblioNetwork(lirt2563, analysis = "co-citation", network = "references", sep = ";")

# Plot the network
#coc_net_lirt2563 <- networkPlot(cocitation_lirt2563, n = 30, Title = "Co-Citation Network", type = "fruchterman", size=T,edgesize = 5)

# cluster results
#coc_net_hec318$cluster_res

```

### 3.2 keyword co-occurrences network (keywords)

```{r}
# Create keyword co-occurrences network

keyword_lirt2563 <- biblioNetwork(lirt2563, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
kco_net_lirt2563 <- networkPlot(keyword_lirt2563, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5)

# cluster results
kco_net_lirt2563$cluster_res
```

## 4 Co-Word Analysis: The conceptual structure of a field

```{r}
# Conceptual Structure using keywords

CS <- conceptualStructure(lirt2563,field="ID", method="MCA", minDegree=5, clust="auto", k.max = 20, stemming=F, labelsize=10, documents=10)

# k-means cluster results
CS$km.res$data.clust
CS$km.res$centers
```